Digital Twins for Ocean Robots

### 2024-11-24 paper/paper.tex
update table

\begin{table}
\tbl{Ocean observing platforms targeted by \pkg{OceanRobots.jl}, and associated data structures (or blank if not yet implemented).}{
\begin{tabular}{|l||r|}\hline
Platform Type & Data Structure\\\hline\hline
surface drifters & \struct{SurfaceDrifter}, \struct{CloudDrift} \\
drifting profilers & \struct{ArgoFloat} \\
moored buoys & \struct{OceanSite}, \struct{NOAAbuoy} \\
sea gliders & \struct{Gliders} \\
expendable bathythermographs & \tbd \\
sea gliders & \struct{Gliders} \\
sail drones & \tbd \\
research vessels & CCHDO \\
ships of opportunity & \tbd \\
orbiting satellites & \struct{SeaLevelAnomaly} \\
suborbital flights & \tbd \\
marine mammals & \tbd \\\hline
\end{tabular}}
\label{tab:robots}
\end{table}

>>>>

\begin{table}
\tbl{Ocean observing platforms targeted by \pkg{OceanRobots.jl}, and associated data structures (or blank if not yet implemented).}{
\begin{tabular}{|l||r|}\hline
Platform Type & Data Structure\\\hline\hline
surface drifters & \struct{SurfaceDrifter}, \struct{CloudDrift} \\
drifting profilers & \struct{ArgoFloat} \\
moored buoys & \struct{OceanSite}, \struct{NOAAbuoy} \\
sea gliders & \struct{Gliders} \\
expendable bathy-thermographs & \tbd \\
sail drones & \tbd \\
\hline
research vessel data & CCHDO \\
ships of opportunity data & \tbd \\
marine mammals & \tbd \\\hline
\end{tabular}}
\label{tab:robots}
\end{table}
